Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-26 snapshot_system/fast14_architecture.tex
revise
update

For example in our tested dataset,  
each VM keeps $h=10$ snapshots and each snapshot adds
about 0.1-4\% of new data. Thus we take ${\Delta u}/{u} \approx 0.02$. For a 40GB snapshot, $u\approx  10$ million.
Then $U=11.8$ million.
We choose  $\epsilon = 0.01$ and $\tau=0.1$.  From Equation~\ref{eq:falserate}, 
each summary vector requires $z=10U=118$ million bits. From Equation~\ref{eq:leakrepair}, 
leak repair should be triggered once for every R=590 runs of approximate deletion. 
When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
only one full leak repair for one physical machine scheduled for every 23.6 days. 
Each repair uses at most  90MB memory on average
%as discussed earlier
and takes a short period of time.

>>>>

For example in our tested dataset,  
each VM keeps $h=10$ snapshots and each snapshot adds
about 0.1-5\% of new data. Thus we take ${\Delta u}/{u} \approx 0.025$. For a 40GB snapshot, $u\approx  10$ million.
Then $U=12.25$ million.
We choose  $\epsilon = 0.01$ and $\tau=0.1$.  From Equation~\ref{eq:falserate}, 
each summary vector requires $z=10U=122.5$ million bits or 15MB. From Equation~\ref{eq:leakrepair}, 
leak repair should be triggered once for every R=490 runs of approximate deletion. 
When one machine hosts 25 VMs and there is one snapshot deletion per day per VM, there would be 
only one full leak repair for one physical machine scheduled for every 19.6 days. 
Each repair uses at most  90MB memory on average
%as discussed earlier
and takes a short period of time.

### 2013-09-26 snapshot_system/fast14_evaluation.tex
update
revise

\begin{table}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem &Read &  Write  & Time  \\ 
    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
    1     & 19\% & 118 & 50 & 8.4 & 1.31\\ \hline
%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
    2     & 35\% & 132 &50  & 9.0 & 1.23\\ \hline
    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
    4     & 63\% & 154&50   & 9.3 & 1.18\\ \hline
%    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks at each machine}
\label{tab:resource_usage}
\end{table}

@@

Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
The dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.02$,
while the top solid line represents the actual leakage measured during the experiment 
with the same $\Delta u/u=0.02$ setting for summary vectors.
After 9 snapshot deletions, the actual leakage reaches 0.0018\% and this means that
there is only 1.8MB space leaked for every 1GB of stored data. 
We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
As this value increases, larger summary vectors are generated thus results in a decrease on the
false-positive ratio, therefore less amount of unused chunks are misjudged.

>>>>

\begin{table}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Tasks & CPU & Mem &Read &  Write  & Time  \\ 
    & & (MB)          &(MB/s) &  (MB/s) & (hrs) \\ \hline
%    1     & 19\% & 118.1 & 50MB/s 8.37 & 1.314\\ \hline
    1     & 19\% & 118 & 50 & 16.4 & 1.31\\ \hline
%    2     & 35\% & 131.8 & 9.0 & 1.226\\ \hline
    2     & 35\% & 132 &50  & 17.6 & 1.23\\ \hline
    %4     & 63\% & 154.1 & 9.3 & 1.179\\ \hline
    4     & 63\% & 154&50   & 18.3 & 1.18\\ \hline
%    6     & 77\% & 171.9 & 9.46 & 1.162\\ \hline
%    8     & 82\% & 90.5 & 89.2 & \\ \hline
%    10                      & 85\% & 97.2   & 90.4 \\ \hline
%    12                      & 91\% & 95.6    & 91.5 \\ \hline
    \end{tabular}
\caption{Resource usage of concurrent backup tasks at each machine}
\label{tab:resource_usage}
\end{table}

@@

Figure~\ref{fig:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.025$,
while the top solid line represents the actual leakage measured during the experiment 
with the same $\Delta u/u=0.025$ setting for summary vectors.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0018 and this means that
there is only 1.8MB space leaked for every 1GB of stored data, it is also obvious that
the leakage grows linearly as we expect. 
We also measure the storage leakage under $\Delta u/u=0.05$ and $0.10$ settings for summary vectors.
As this value increases, larger summary vectors are generated thus results in a decrease on the
false-positive ratio, therefore less amount of unused chunks are misjudged.
